Investing in infants: the lasting effects of cash transfers to new families

### 2024-07-31 posts/BarrEgglestonSmith/BarrEgglestonSmith2022.qmd
Added research question page to BarrEgglestonSmith2022.html

::: {.incremental}
* Exam score $\sigma$&uarr; \rArr; $2500&uarr; at age 28 per year [@ChettyFriedmanRockoff2014b]  
* .037$\sigma$ (per \$1000)$\times$ $2500=$92 per year per $1000 spent  
   * 9.2% is pretty high...   
* "(C)ould entirely account for our observed wage effects ... $353 per $1000" (?)  
:::

>>>>

::: {.incremental}
* Exam score $\sigma$&uarr; &rArr; $2500&uarr; at age 28 per year [@ChettyFriedmanRockoff2014b]  
* .037$\sigma$ (per \$1000)$\times$ $2500=$92 per year per $1000 spent  
   * 9.2% is pretty high...   
* "(C)ould entirely account for our observed wage effects ... $353 per $1000" (?)  
:::
